Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-06-20 MCQMC2022ChallengesQMCSoftwareArticle_revision_1.tex
SC: add non-code contribution in open source

@@

\SCComment{Response to comment \#4:  Python is known for its versatility, but it can be slower than highly optimized implementations in languages like Java or C++.  For QMCPy developers, it would be beneficial to investigate such underlying interfaces or consider other code acceleration techniques by leveraging Numba, Joblib, or Ray in the future.
}

>>>>

\SCComment{In QMCPy, we recognize the crucial role of non-code contributors to the project~\cite{K23}. Besides coding,  we also need documentation, interface design, testing, community management, and release management. These non-code contributions help make the project more  accessible. Non-coding roles offer opportunities for individuals with less coding experiences to develop technical and non-technical skills over time.  Additionally, the emergence of no-code or low-code analytical platform such as SAS Studio and SAS Viya offer a chance for individuals who are less experienced with complex coding to learn and contribute in a more user-friendly environment.  We need and welcome non-code contributors to work alongside code contributors, enhancing the overall health of the project and the diversity of the community. }

@@

\SCComment{Response to comment \#4:  Python is known for its versatility, but it can be slower than highly optimized implementations in languages like Java or C++.  For QMCPy developers, it would be beneficial to investigate such underlying interfaces or consider other code acceleration techniques by leveraging high-performance libraries such as Numba, JAX, Joblib, or Ray in the future.
}
